---
title: "PSY 8712 Week 12 Project"
author: "Jessica Wang"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Script Setting and Resources
```{r}
library(tidyverse)
library(RedditExtractoR)
library(tm)
library(textstem)
library(RWeka)
library(topicmodels)
library(ldatuning)
library(doParallel)
library(tidytext)
library(topicmodels)
library(wordcloud)
library(caret)
library(randomForest)
```

## Data Import and Cleaning
```{r}
#week12_tbl <- find_thread_urls(subreddit = "IOPsychology", period = "year") %>%
  #{get_thread_content(.$url)} %>%
  #.$threads %>%
  #select(title, upvotes = score) %>%
  #as_tibble()

#write_csv(week12_tbl, "../data/week12_tbl.csv")

week12_tbl <- read_csv("../data/week12_tbl.csv")
```
ˆ
```{r}
#creating corpus
io_corpus_original <- VCorpus(VectorSource(week12_tbl$title)) 

preprocess_corpus <- function(corpus) {
  corpus %>%
    tm_map(content_transformer(tolower)) %>%
    tm_map(removePunctuation) %>%
    tm_map(removeNumbers) %>%
    tm_map(removeWords, c(stopwords("en"), "io", "psychology", "iopsychology", "riopsychology")) %>%
    tm_map(stripWhitespace) %>%
    tm_map(content_transformer(lemmatize_strings))
}

#apply preprocessing
io_corpus <- preprocess_corpus(io_corpus_original)

#comparing
compare_them = function(corpus1, corpus2){
  select_index = sample(1:length(io_corpus$content), 1)
  original_row = corpus1[[select_index]]$content
  cleaned_row = corpus2[[select_index]]$content
  return(data.frame(original_title = original_row,
                   cleaned_title = cleaned_row))
}
compare_them(io_corpus_original, io_corpus)

#remove empty
io_corpus_filt <- tm_filter(io_corpus, FUN = function(x) { return(nchar(stripWhitespace(x$content)[[1]]) > 0) } )
```

```{r}
#define a custom tokenizer for unigrams and bigrams
myTokenizer <- function(x) {
  NGramTokenizer(x, Weka_control(min = 1, max = 2))
}

#create the Document-Term Matrix with the custom tokenizer
io_dtm_empty <- DocumentTermMatrix(io_corpus, control = list(tokenize = myTokenizer))

#sum tokens in each document to identify empty documents
tokenCounts <- apply(io_dtm_empty, 1, sum)

#filter out the documents with zero tokens
io_dtm <- io_dtm_empty[tokenCounts > 0, ]

#optionally, save the indices of documents with zero tokens for future reference
indices_zero <- which(tokenCounts == 0)  # More direct approach
zero_elements <- length(indices_zero)  # Number of empty documents

#convert DTM to a tibble for further manipulation or inspection
io_dtm_tbl <- as.data.frame(as.matrix(io_dtm)) %>% 
  tibble::as_tibble()

#remove sparse terms from the DTM to create a slimmer version
sparse_threshold <- 0.997  # Keeping terms that appear in at least 0.3% of documents
io_slim_dtm <- removeSparseTerms(io_dtm, sparse = sparse_threshold)

#convert the slim DTM to a tibble
io_slim_dtm_tbl <- as.data.frame(as.matrix(io_slim_dtm)) %>%
  tibble::as_tibble()
```

## Analysis
```{r}
tuning <- FindTopicsNumber( 
io_dtm, 
topics = seq(2,15,by=1), 
metrics = c("Griffiths2004", 
"CaoJuan2009", 
"Arun2010", 
"Deveaud2014"),
verbose = T,
control = list(seed = 123),
mc.cores = 6L 
)

#5 clusters seems best
FindTopicsNumber_plot(tuning)

io_lda <- LDA(io_dtm, k=5)

tidy(io_lda, matrix="beta") %>% 
  group_by(topic) %>%
  top_n(10, beta) %>%
  arrange(topic, -beta) 

topics_tbl <- tidy(io_lda, matrix="gamma") %>%
  group_by(document) %>%
  top_n(1, gamma) %>%  # Get the top topic by highest probability for each document
  slice(1) %>%
  ungroup() %>%
  rename(doc_id = document, probability = gamma) %>%
  mutate(doc_id = as.numeric(doc_id)) %>%
  arrange(doc_id)

#directly associate titles from `week12_tbl` using row indices
topics_tbl <- topics_tbl %>%
  mutate(original = week12_tbl$title[doc_id])
```

## Questions
###1. 
Topic 1: Career and Education in Psychology. This topic seems to center around career-related queries and educational paths in psychology. Key terms include "job," "psych," "career," "psychologist," "grad," "internship," and "interview." It suggests a focus on professional development and educational opportunities in the field of psychology.
Topic 2: Professional Events and Networking. The terms such as "work," "assessment," "conference," "siop", and "practitioner" suggest a theme related to professional gatherings, assessments in the workplace, and networking within the professional community.
Topic 3: Academic Research. Highlighted by terms like "research," "study," and "graduate," this topic appears to focus on academic research and studies.
Topic 4: Consulting and Career Advice. Terms like "advice," "consult," "career," "path," and "interview" suggest a focus on consulting practices and career advice, possibly providing guidance on career paths and job search strategies.
Topic 5: Community and Discussions. Terms like "discussion," "read," "master," and "think,"likely reflects regular community discussions or threads, possibly in a recurring series, focusing on a variety of topical issues within the psychology community.

###2. 
They match decently, showing some content validity. There are some that don't line up perfectly, but I think that's to be expected

```{r}
week12_tbl <- week12_tbl %>%
  mutate(doc_id = row_number())

#join topics_tbl with week12_tbl based on doc_id
final_tbl <- left_join(topics_tbl, week12_tbl, by = "doc_id")

#statistical analysis, no significant difference
summary(lm(upvotes~topic,data=final_tbl))

#machine learning analysis, The RMSE values are quite high relative to the range of upvote counts (assuming a typical range of upvotes). This suggests that the model, while potentially offering some insight, is not highly accurate in predicting exact upvote numbers.
#ensure the topic is a factor and upvotes are numeric
final_tbl$topic <- as.factor(final_tbl$topic)
final_tbl$upvotes <- as.numeric(final_tbl$upvotes)

#splitting data into training and testing sets
set.seed(123)  # For reproducibility
training_indices <- createDataPartition(final_tbl$upvotes, p = 0.8, list = FALSE)
training_data <- final_tbl[training_indices, ]
testing_data <- final_tbl[-training_indices, ]

#training control setup
fitControl <- trainControl(
  method = "cv",   # Cross-validation
  number = 10      # Number of folds
)

# Train the model
model <- train(
  upvotes ~ topic,
  data = training_data,
  method = "rf",
  trControl = fitControl,
  tuneLength = 3  # Tune over 3 different values of mtry
)

# Output model details
print(model$results)

# Predict on the testing data
predictions <- predict(model, testing_data)

# Calculate RMSE for the test set
test_rmse <- RMSE(predictions, testing_data$upvotes)
cat("Test RMSE: ", test_rmse, "\n")
```

## Visualization
```{r}
#wordcloud
wordcloud(
  words = names(io_dtm_tbl),
  freq = colSums(io_dtm_tbl),
  max.words = 25
)
```






